ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-09-28 rebuttal.tex

\begin{reviewer}
    %
    ``Moreover, the standard remains closed, requiring potential users to register with the
    standard's authors to access the specification and the growing database.''

    I suggest instead:

    ``Registration is open for everyone who provides a valid institutional e-mail address.''
    %
\end{reviewer}

\begin{response}
    We have updated the text to reflect this information; however, we argue that requiring 
    registration limits use and differs from the openness ``baked-in'' to our approach.
\end{response}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Reviewer \#2:}

\begin{reviewer}
    %
    My main concern with the creation of a publically available database, formatted with ChemKED, is
    that it seems that the creation of the files has to be done manually, i.e. susceptible for
    errors. This is especially true if the experiment comprises a big set of datapoints and/or
    hundreds of measured species. Furthermore, the YAML data serialization format is indeed
    human-readable, but it does not provide an easy summary/overview of the experimental data, such
    as an excel or CSV file would give, and therefore, people might be not willing to put the extra
    effort.
    %
\end{reviewer}

\begin{reviewer}
    %
    1.~How are the authors planning on `forcing' the experimentalists to publish their data in this
    new ChemKED file format?
    %
\end{reviewer}

\begin{response}
    %
    While we cannot force anyone to use a particular format, we hope that by defining a format and
    ecosystem with desirable features---including inherent openness and usability---experimentalists
    will begin adopting a community-standard format. In fact, we have already received interest from
    various groups, and hope this will grow as we continue to improve and add features. We also hope
    that at a certain point, with wide adoption, sharing experimental data in a standard format will
    become the expected norm (e.g., when submitting an article for publication) like sharing a
    Chemkin-format chemical kinetic model.

    Furthermore, we are willing to work (and currently are) with experimentalists to provide them easy-to-use
    conversion scripts from internal data formats, and they will help us define what needs to go in the
    specification for their experiment.
    %
\end{response}

### 2017-09-28 pyked.tex
add Bryan's suggested text and rebuttal for #12

More recently, Varga and coworkers~\autocite{Varga2015a,Varga2017} developed the
ReSpecTh standard, which builds on the PrIMe format. ReSpecTh adds important
features that make files better standalone representations of experimental
data---i.e., more informative by themselves rather than in concert with a larger
system. For example, where PrIMe uses internal bibliographic references,
ReSpecTh adds a field for typical bibliographic data. The ReSpecTh standard also
provides machine-readable formats for describing ignition experiments, including
a field for the definition of autoignition and the ability to specify
facility-specific effects. However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same usability issues as PrIMe.
Moreover, the standard remains closed, requiring potential users to register
with the standard's authors to access the specification and the growing database.

>>>>

More recently, Varga and coworkers~\autocite{Varga2015a,Varga2017} developed the
ReSpecTh standard, which builds on the PrIMe format. ReSpecTh adds important
features that make files better standalone representations of experimental
data---i.e., more informative by themselves rather than in concert with a larger
system. For example, where PrIMe uses internal bibliographic references,
ReSpecTh adds a field for typical bibliographic data. The ReSpecTh standard also
provides machine-readable formats for describing ignition experiments, including
a field for the definition of autoignition and the ability to specify
facility-specific effects. However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same usability issues as PrIMe.
Moreover, the standard remains inaccessible to the public, requiring potential users
to register with the standard's authors using a valid institutional email address
to access the specification and the growing database.
